Time Series Modeling of Varying Complexity Captures Subdiffusive Solute Dynamics and Predicts Long Timescale Behavior in Nanoscale Pores.

### 2019-10-21 Ben_Manuscripts/stochastic_transport/Draft.tex
Updates to intro + methods, incorporating methanol and acetic acid

\title{Time Series Modeling of Subdiffusive Solute Transport in an H\textsubscript{II}
 Phase Lyotropic Liquid Crystal Membrane}
%MRS1: I wonder if ``Times series modeling'' is better?  We should keep thinking about a better term.  Stochastic modeling is such a general term, it encompasses a lot  . . . 
%MRS4: can we turn this into a thesis statement (we find X) rather than a topic statement (we studied X).  Something about the complexity of the models required to get the subdiffusive behavior right?
\author{Benjamin J. Coscia \and Michael R. Shirts}

@@

@@

  Three well-known classes of behavior leading to anomalous subdiffusion are 
  continuous time random walks (CTRW), fractional Brownian motion
  (FBM) and random walks on fractals (RWF).\cite{meroz_toolbox_2015}
  The theory is frequently used to describe single particle trajectories.~\cite{morrin_three_2018,metzler_anomalous_2014}
  %BJC4: consider rewording sentence below
  A CTRW is characterized by a distribution of hop lengths and dwell times, 
  where trajectories are characterized by independent random draws from 
  each distribution.\cite{montroll_random_1965} FBM is common in crowded,
  viscoelastic environments where each jump comes from a Gaussian distribution
  but is anti-correlated to its previous step.~\cite{mandelbrot_fractional_1968,jeon_fractional_2010,banks_anomalous_2005}
  An RWF is imposed by a system's geometry. Systems with tortuous pathways 
  and dead ends cause anti-correlated motion.\cite{meroz_toolbox_2015,neusius_subdiffusion_2008}
  These processes can occur alone or in combination.

  %BJC4: should I mention which anomalous subdiffusion model we chose? 
  Our first modeling approach is based on the anomalous diffusion literature, 
  applying the mathematical formalism describing subdiffusive transport to observed
  solute trajectories. We fit anomalous diffusion models in two ways: 
  %MRS4: can you clarify the sentence below?  Probably something like: uses a single set of parameters in the diffusion equations, etc.
  %BJC4: see if below helps.
  %First, based on a single set of parameters. 
  First, we parameterized solute motion using a single set of parameters fit
  to a hypothesized anomalous diffusion model. Second, we use a two-state approach
  extracting two sets of model parameters calculated based on a solute's radial
  distance from the closest pore center.

  %BJC4: might want to change the theme of this paragraph to something like: 
  % Anomalous diffusion can help uncover mechanisms. Once we know mechanisms, we 
  % can define them as states and use the MSDDM.
  While elegant, pure anomalous diffusion theory may in some cases give only a 
  qualitative understanding of transport mechanisms. 
  %MRS4: might need to provide a bit more explanation why it would be ony qualitative.  
  %Relating it to molecular scale behavior and examples might help.
  %BJC4: mention ageing
  %BJC4: ?
  Complex temporal relationships in 
  between hops may have a significant effect on the average MSD. Inhomogeneity of 
  a medium or multiple types of interactions may lead to a number of distinct 
  diffusive regimes. In this case, a state based model may be useful.

@@

  %BJC4: making goals more explicit
  The success of our modeling approaches can be defined in two ways. First, if we
  can closely reproduce solute MSDs measured from MD simulations with realizations
  of our models, then it is likely that the model sufficiently captures solute 
  dynamics and can be used in a predictive capacity. Even if a model fails to 
  reproduce the MD MSDs, there is value in uncovering the cause of the deviation.
  The second measure of success is by analysis of the parameters defining each 
  model. The parameters themselves should provide clues that help explain solute 
  behavior in a coherent way. A model that successfully reproduces MD MSDs, but 
  with nonsensical parameters has severely diminished value.

@@

  %BJC4: missing something about predictive capabilities

@@

@@

  % BJC3: x --> z since I'm measuring diffusion in the z direction?
  % MRS4: reasonable change.  Or explicitly state that you will refer to the pore axis as x. 
  % BJC4: I think it'll be less confusing to me writing it to change it to z. Is it worth
  % explicitly stating that z is the positional coordinate.
  Solutes in this system exhibit subdiffusive behavior, a type of anomalous diffusion.
  During an anomalous diffusion process, the mean squared displacement (MSD)
  does not grow linearly with time, rather it follows a power law of the form:
  \begin{equation} 
  \langle z^2(t) \rangle = K_{\alpha_d}t^{\alpha_d}
  \label{eqn:msd_form}
  \end{equation} 
  where $\alpha_d$ is the anomalous exponent and $K_{\alpha_d}$ is the generalized 
  diffusion coefficient. A value of $\alpha_d < 1$ indicates a subdiffusive process, 
  while values of $\alpha_d = 1$ and $\alpha_d > 0$ are characteristic of Brownian and
  superdiffusive motion respectively.

  %BJC3: removed ensemble MSD because it's not used
  We analyzed the time-averaged MSD of the simulated trajectories by measuring
  all possible displacements over time lag $\tau$:
  \begin{equation}
  \overline{z^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (z(t + \tau) - z(t))^2 dt
  \end{equation}
  where T is the length of the trajectory. Note that only the \textit{ensemble} MSD
  will reproduce the form of Equation~\ref{eqn:msd_form} in all cases. 
  %MRS4: probably need to explain in what way it is non-ergodic below, and if this is the scenario that people should care about.
  %BJC4: reworded, defined ergodicity (usually called 'weak' ergodicity breaking in literature) and
  % explained why it's not important for this study.
  In a pure CTRW, for example, the power law distribution of trapping times leads to
  weak ergodicity breaking. The time-averaged MSD is linear while the ensemble averaged
  MSD has the form of Equation~\ref{eqn:msd_form}.~\cite{meroz_toolbox_2015} With power
  law trapping behavior, the time between hops diverges so there is no characteristic
  measurement time scale of solute motion. In fact, as measurement time increases, the 
  MSD of a CTRW tends to decrease, a phenomenon called aging, because trajectories 
  with trapping times on the order of the measurement time get incorporated into the 
  calculation.~\cite{bel_weak_2005} We chose to analyze just the time-averaged MSD 
  because we it is a more statistically robust measure of the average distance a solute
  travels over time versus the ensemble average. Although theoretically possible, we do
  not use the MSD to calculate $\alpha_d$ because we can extract the same parameter 
  with higher precision using the dwell time distributions as described below.

@@

  \textit{Dwell time distributions:} For subdiffusive transport, the distribution 
  of dwell times is expected to fit a power law distribution 
  proportional to $t^{-1-\alpha_d}$.~\cite{meroz_toolbox_2015}
  %BJC3: is it okay to leave above equation in line? Or should it get numbered?
  %BJC3: I added subscript d to the dwell time alpha because alpha is a standard parameter for power laws and levy stable distributions
% BJC3: following includes normalization constant 
%  of the form:
%  \begin{equation}
%  (\beta - 1)x_{min}^{\beta - 1}x^{-\beta}
%  \end{equation}  
%  where $\beta = (1 + \alpha)$ and $x_{min}$ is the smallest measured value of $x_i$.~\cite{meroz_toolbox_2015,clauset_power-law_2009}
%  proportional to $t^{-1-\alpha}$.~\cite{meroz_toolbox_2015}
  Because we are limited to taking measurements at discrete values dictated by the output 
  frequency of our simulation trajectories, we fit the empirical dwell times
  to a discrete power law distribution whose maximum likelihood $\alpha_d$ 
  parameter we calculated by maximizing the following likelihood function: 
  \begin{equation}
	\mathcal{L}(\beta) = -n\ln \zeta(\beta, t_{min}) -
	\beta\sum_{i=1}^{n} \ln t_i 
  \label{eqn:powerlaw_likelihood}
  \end{equation}
  where $\beta = 1 + \alpha_d$, $t_i$ are collected dwell time data points,
  $n$ the total number of data points, and $\zeta$ is the Hurwitz zeta function
  where $t_{min}$ is the smallest measured value of	$t$.~\cite{clauset_power-law_2009}

@@

  % BJC3: Making a logical argument regarding how we estimate H here is important
  % because I haven't seen anyone do it this way.
  sFBM implies correlated hops which we describe using the Hurst parameter, $H$. 
  The autocovariance function of hop lengths has the analytical form:~\cite{mandelbrot_fractional_1968}
  \begin{equation}
    \gamma(k) = \dfrac{\sigma^2}{2}\bigg[|k-1|^{2H} - 2|k|^{2H} + |k+1|^{2H}\bigg]
  \label{eqn:fbm_autocorrelation}
  \end{equation}
  where $\sigma^2$ is the variance of the underlying Gaussian distribution from which hops are
  drawn and $k$ is the time lag, or number of increments between hops. The hop autocorrelation
  function is simply Equation~\ref{eqn:fbm_autocorrelation} normalized by the variance. 
  When $H < 0.5$, hops are negatively correlated, when $H = 0.5$ we recover Brownian motion
  and when $H > 0.5$, one observes positive correlation between hops. There are many methods
  for estimating the Hurst parameter for a time series.~\cite{clegg_practical_2006} It can
  be a difficult task because Equation~\ref{eqn:fbm_autocorrelation} decays slowly to zero, 
  especially when $H > 0.5$, meaning one needs to study large time lags with high frequency.
  Fortunately (from a mathematical perspective), all of our solutes show anti-correlated motion, so most of the information in
  Equation~\ref{eqn:fbm_autocorrelation} is contained within the first few time lags (see 
  Figure~\ref{S-fig:hurst_autocorrelation} of the Supporting Information). Any hope of
  fitting longer time lags to our data is lost in the noise since the analytical values
  are so close to zero. Therefore, we obtained H by performing a least squares fit of 
  Equation~\ref{eqn:fbm_autocorrelation} to the first 10 lags of the empirically measured
  autocorrelation function.

@@

  We observe different dynamical behavior when solutes move while inside 
  the pore versus while in the tail region. This inspired two anomalous diffusion 
  models of varying complexity. We created a simple, single mode model with a single 
  set of parameters fit to solute trajectories.
%  $\alpha$, $\sigma$, $H$ and, when the truncated power law is used, $\lambda$ parameters
%  fit to solute trajectories.
  Our second, two mode model assigns a set of parameters to each of 2 modes based
  on the solute's radial location. Solutes in mode 1 are in the pore region, defined
  %MRS4: some justification on why 0.75 vs. any other cutoff.
  %BJC4: I justified sentence after next. Is there something more I should say? 
  as less than 0.75 nm from any pore center. All else are in mode 2, the tail region. 
  We determined this cut-off by maximizing the difference in dynamical behavior as 
  described in our previous work.~\cite{coscia_chemically_2019} Unfortunately, 
  there were not enough sufficiently long sequences of hops in each mode to reliably
  calculate a Hurst parameter for each mode so we used the Hurst parameter from the 
  single mode model for both modes of the two mode model.

@@

  We simulated models with all combinations of the types of dwell and hop length
  distributions described above, which are summarized in Table~\ref{table:anomalous_models}.
  All models include correlation between hops.
  %MRS4: not abbreviations are not necessarily defined: should be defined above, perhaps? (i.e. we will refer X as 'sFBMcut')
  \begin{table}[!htb]
	  \centering
	  \begin{tabular}{|c|c|c|}
	  \hline
	  Dwell Distribution                & Hop Length Distribution & Abbreviation \\
	  \hline
      Power Law                         & Gaussian                & sFBM         \\
      Power Law w/ Exponential Cut-off  & Gaussian                & sFBMcut      \\
      Power Law                         & L\'evy Stable           & sFLM         \\
      Power Law w/ Exponential Cut-off  & L\'evy Stable           & sFLMcut      \\
	  \hline
	  \end{tabular}
	  \caption{We tested models with various modifications to the dwell and hop
	  length distributions. We incorporate correlation structure into all models.}\label{table:anomalous_models}
 \end{table}

  % BJC3: will need to modify this text to reflect different lengths of simulations
  For each solute, we simulated 10000 anomalous diffusion trajectories of length
  $T_{sim}$ in order to directly compare our model's predictions to MD simulations.
  $T_{sim}$ varied due to differing solute equilibration times. We constructed 
  trajectories by simulating sequences of dwell times and correlated hop lengths
  generated based on parameters randomly chosen from our bootstrapped parameter 
  distributions. We propagated each trajectory until the total time equaled or 
  exceeded $T_{sim}~ \mu$s, then truncated the last data point so that the total 
  time exactly equaled $T_{sim}~ \mu$s since valid comparisons are only possible 
  between fixed length sFBM simulations. 
  % BJC4: removed following sentence because I talk about aging above
  %The power law dwell time behavior gives rise to the aging phenomenon, embodied by a 
  %decrease in MSD with measurement time.~\cite{neusius_subdiffusion_2008,metzler_anomalous_2014}
  We reported the time-averaged MSD after time lags 40\% the length of the trajectory
  with corresponding 95\% intervals.
  %BJC3: Not sure if 40 % above is too long. I could do 20
  %MRS4: is there some rule of thumb that could be used to justify the choice?
  When simulating 2 mode models, we determined the state sequence based on random 
  draws weighted by the appropriate row of the probability transition matrix. We 
  %MRS4: not quite sure what you mean by incorporating uncertainty. 
  %BJC4: The Dirichlet distribution basically perturbs the transition probabilities
  % by an amount proportional to the number of observations. So things that don't
  % get transition to/from frequently will have higher uncertainty. Output of 
  % draw form Dirichlet distribution sums to 1. It doesn't really change the results
  % much but I think it's good practice. In the 2D case, it is just a beta distribution
  incorporated uncertainty into transition probabilities by drawing samples from a 
  two dimensional Dirichlet distribution (also called a beta distribution) with concentration parameters defined by 
  the count matrix.~\cite{bacallado_bayesian_2009} We drew hops and dwells based on
  the current state of the system.

@@

  %We also projected MSDs out to 1 second for each solute. % BJC3:??
  %BJC3: not sure how to cite fbm
  We used the python package \texttt{fbm} to generate exact simulations of FBM and our
  own python implementation of the algorithm by Stoev and Taqqu to simulate FLM.
  ~\cite{stoev_simulation_2004} Note that, to our knowledge, there are no known exact
  simulation algorithms for generating FLM trajectories, however, the algorithm
  we used sufficiently approximates draws from the marginal distribution and 
  reasonably approximates the correlation structure. We added an empirical correction
  to enhance the accuracy of the correlation structure (see Section~\ref{S-section:flm_correlation}
  of the Supporting Information for validation of the approach).

@@

  When simulating MD-length FLM trajectories, we limited the maximum hop length based on where
  the empirical hop distribution began to significantly under-sample the theoretical
  maximum likelihood estimate (MLE) L\'evy stable distribution (see 
  Section~\ref{S-section:truncation} of the Supporting Information).

  % TODO?: This vvvv
  For our 1 second simulations, we limited the maximum hop length to that seen by
  the same solute undergoing Brownian motion in an unconfined aqueous environment. 
  We have no reason to believe there is any kind of facilitated diffusion, so 
  excursions characteristic of Brownian motion represent a reasonable upper limit
  on hop lengths. To determine these limits we placed 24 solutes in a cubic box of 
  water, 4 nm on each side. We allowed the solutes to diffuse for 100 ns, more than
  ensuring the mean squared displacement entered a linear regime. We recorded the largest
  observed hop length over a 0.5 ns time lag.

@@

  A Markov state model (MSM) decomposes a time series into a set of discrete states
  with transitions between states defined by a transition probability matrix, $T$,
  which describes the conditional probability of jumping to a specific state given
  the previously observed state.~\cite{pande_everything_2010,wehmeyer_introduction_2018}
  Software packages such as MSMbuilder~\cite{beauchamp_msmbuilder2:_2011} and 
  pyEMMA~\cite{scherer_pyemma_2015} provide work flows capable of featurization and
  dimensional reduction.

@@

  %MRS4: here, be more explicit you are testing the validity of the Markovian approximation on the molecular data.
  %BJC4: Tried to clarify in thesis statement. Let me know if you think it needs more
  We verified the Markovianity of state transitions observed in our simulations 
  by analyzing the empirically measured transition matrix. An important condition
  of a Markov process is the satisfaction of detailed balance:
  \begin{equation}
  T_{i,j}P_i(t=\infty) = T_{j,i}P_j(t=\infty)
  \end{equation}
  where $P$ is the equilibrium distribution of states. In other words, the number of
  transitions from state $i$ to $j$ and from state $j$ to $i$ should be equal. A second
  test is to verify that $T$ holds up to coarser time scales. As long as solutes
  sufficiently sample the states in Table~\ref{table:states}, $T$ should be invariant
  with time.~\cite{swope_describing_2004} We verified these properties 
  in Section~\ref{S-section:markov_validation} of the Supporting Information.

@@

@@

>>>>

\title{Time Series Modeling of Varying Complexity Captures Subdiffusive Solute Dynamics
and Predicts Long Timescale Behavior in Nanoscale Pores.}
%MRS1: I wonder if ``Times series modeling'' is better?  We should keep thinking about a better term.  Stochastic modeling is such a general term, it encompasses a lot  . . . 
%MRS4: can we turn this into a thesis statement (we find X) rather than a topic statement (we studied X).  Something about the complexity of the models required to get the subdiffusive behavior right?
\author{Benjamin J. Coscia \and Michael R. Shirts}

@@

  %BJC4: Added next two paragraphs to help ease more into time series modeling
  So far, our molecular models have provided valuable qualitative mechanistic insight 
  with some quantitative support which already allows us to speculate about new LLC
  monomer designs, however they would be of greater value to a wider audience if we 
  could provide quantitative predictions of macroscopic observables such as solute 
  flux. Due to the size of the system we are studying ($\sim$62,000 atoms) it is 
  prohibitively expensive and time-consuming to run simulations longer than 
  those performed for this work ($\sim$5 $\mu$s). And even with the relatively large 
  size of our system, we only simulate 24 solute trajectories per unit cell in order
  to minimize solute-solute interactions. This results in relatively high uncertainties
  in observables such as mean squared displacement (MSD), preventing reliable long
  timescale predictions. We are in need of a way of studying the collective motion
  of a much larger set of solute over much longer timescales.

  By reducing our MD simulations to observations of several key properties that 
  have the greatest influence on solute dynamics, we can construct many realizations
  of single solute trajectories useful for making long timescale predictions with 
  computational ease and lower uncertainties. Fortunately, there is an abundance of 
  information encoded in the complex solute trajectories. Into our model, we can 
  incorporate fluctuations and time-dependent correlations in solute position as well
  as the length of time solutes are trapped. We can add further detail by integrating
  our time series analysis with our knowledge of the primary trapping mechanisms as
  well as the solute's changing chemical environment within the heterogeneous membrane.

@@

  Three well-known classes of behavior leading to anomalous subdiffusion are 
  continuous time random walks (CTRW), fractional Brownian motion
  (FBM) and random walks on fractals (RWF).\cite{meroz_toolbox_2015}
  These types of motion are frequently used alone or in combination to describe
  single particle trajectories.~\cite{morrin_three_2018,metzler_anomalous_2014}
  %BJC4: consider rewording sentence below
  A CTRW is characterized by a distribution of hop lengths and dwell times, 
  where trajectories are characterized by sequential independent random draws from 
  each distribution.\cite{montroll_random_1965} FBM is common in crowded,
  viscoelastic environments where each jump comes from a Gaussian distribution
  but is anti-correlated to its previous step.~\cite{mandelbrot_fractional_1968,jeon_fractional_2010,banks_anomalous_2005}
  An RWF is imposed by a system's geometry. Systems with tortuous pathways 
  and dead ends cause anti-correlated motion.\cite{meroz_toolbox_2015,neusius_subdiffusion_2008}

  %BJC4: added mention of the anomalous subdiffusion model we chose 
  Our first modeling approach is based on the anomalous diffusion literature, 
  applying the mathematical formalism describing subdiffusive transport to observed
  solute trajectories. Specifically, we treated our system as an FBM process subordinate
  to a CTRW, or subordinated FBM (sFBM) for short. We fit sFBM
  models in two ways: 
  %MRS4: can you clarify the sentence below? Probably something like: uses a single set of parameters in the diffusion equations, etc.
  %BJC4: see if below helps.
  %First, based on a single set of parameters. 
  First, we parameterized solute motion using a single set of parameters fit
  to a hypothesized anomalous diffusion model. Second, we used a two-state approach
  by extracting two sets of model parameters calculated based on a solute's radial
  distance from the closest pore center. We observe different dynamical behavior of
  solute within the pore region versus within the monomer tails.

  Where applicable, the sFBM model is an elegant way to characterize single 
  particle trajectories and in addition to providing an easy and efficient way to 
  simulate solute trajectories, can be helpful in uncovering the underlying 
  solute-membrane interactions which result in observed transport mechanisms.
  It can help researchers formulate hypotheses to explain why a certain set of
  parameters is characteristic to a specific solute. This is largely the approach
  we used to discover the three primary trapping mechanisms in our previous work.~\cite{coscia_chemically_2019}
  Once one has knowledge of the primary mechanisms leading to anomalous diffusion
  behavior, one may gain additional insight by formulating a state-based model.

  %BJC4: Replaced below paragraph with above. 
%  While elegant, pure anomalous diffusion theory may in some cases give only a 
%  qualitative understanding of transport mechanisms. 
%  %MRS4: might need to provide a bit more explanation why it would be ony qualitative.  
%  %Relating it to molecular scale behavior and examples might help.
%  %BJC4: mention ageing
%  %BJC4: ?
%  Complex temporal relationships in 
%  between hops may have a significant effect on the average MSD. Inhomogeneity of 
%  a medium or multiple types of interactions may lead to a number of distinct 
%  diffusive regimes. In this case, a state based model may be useful.

@@

  %BJC4: making goals more explicit
  The success of our modeling approaches can be defined in two ways. First, if we
  can closely reproduce solute MSDs measured from MD simulations with realizations
  of our models, then it is likely that the model sufficiently captures solute 
  dynamics and can be used in a predictive capacity. Even if a model fails to 
  reproduce the MD MSDs, there is value in uncovering the cause of the deviation.
  The second measure of success is by analysis of the parameters defining each 
  model. The parameters themselves should provide clues that help explain solute 
  behavior in a coherent way. A model that successfully reproduces MD MSDs, but 
  with nonsensical parameters has severely diminished value as it could be a 
  consequence of luck.

@@

@@

  %BJC4: new
  We find that the sFBM anomalous diffusion model does the best job of reproducing
  simulation behavior of all solutes studied. Therefore, we use it to demonstrate 
  how one could predict solute flux through a theoretical pore of with an 
  experimentally relevant length.

@@

  % BJC3: x --> z since I'm measuring diffusion in the z direction?
  % MRS4: reasonable change.  Or explicitly state that you will refer to the pore axis as x. 
  % BJC4: I think it'll be less confusing to me writing it to change it to z.
  Solutes in this system exhibit subdiffusive behavior, a type of anomalous diffusion.
  During an anomalous diffusion process, the mean squared displacement (MSD)
  does not grow linearly with time, rather it follows a power law of the form:
  \begin{equation} 
  \langle z^2(t) \rangle = K_{\alpha_d}t^{\alpha_d}
  \label{eqn:msd_form}
  \end{equation} 
  where $\alpha_d$ is the anomalous exponent and $K_{\alpha_d}$ is the generalized 
  diffusion coefficient. We only calculate MSD with respect to the solutes' center of
  mass $z$-coordinate, which is oriented along the pore axis. A value of $\alpha_d < 1$
  indicates a subdiffusive process, while values of $\alpha_d = 1$ and $\alpha_d > 0$ 
  are characteristic of Brownian and superdiffusive motion respectively.

  %BJC3: removed ensemble MSD because it's not used
  We analyzed the time-averaged MSD of the simulated trajectories by measuring
  all possible displacements over time lag $\tau$:
  \begin{equation}
  \overline{z^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (z(t + \tau) - z(t))^2 dt
  \end{equation}
  where T is the length of the trajectory. Note that only the \textit{ensemble} MSD
  will reproduce the form of Equation~\ref{eqn:msd_form} in all cases. 
  %MRS4: probably need to explain in what way it is non-ergodic below, and if this is the scenario that people should care about.
  %BJC4: reworded, defined ergodicity (usually called 'weak' ergodicity breaking in literature) and
  % explained why it's not important for this study.
  In a pure CTRW, for example, the power law distribution of trapping times leads to
  weak ergodicity breaking. The time-averaged MSD is linear while the ensemble averaged
  MSD has the form of Equation~\ref{eqn:msd_form}.~\cite{meroz_toolbox_2015} With power
  law trapping behavior, the time between hops diverges so there is no characteristic
  measurement time scale of solute motion. In fact, as measurement time increases, the 
  MSD of a CTRW tends to decrease, a phenomenon called aging, because trajectories 
  with trapping times on the order of the measurement time get incorporated into the 
  calculation.~\cite{bel_weak_2005} We chose to analyze just the time-averaged MSD 
  because, compared to the ensemble average, it is a more statistically robust measure
  of the average distance a solute travels over time. Although theoretically possible, we do
  not use the MSD to calculate $\alpha_d$ because we can extract the same parameter 
  with higher precision using the dwell time distributions as described below.

@@

  \textit{Dwell time distributions:} For subdiffusive transport, the distribution 
  of dwell times is expected to fit a power law distribution 
  proportional to $t^{-1-\alpha_d}$.~\cite{meroz_toolbox_2015}
  %BJC3: is it okay to leave above equation in line? Or should it get numbered?
  %BJC3: I added subscript d to the dwell time alpha because alpha is a standard parameter for power laws and levy stable distributions
% BJC3: following includes normalization constant 
%  of the form:
%  \begin{equation}
%  (\beta - 1)x_{min}^{\beta - 1}x^{-\beta}
%  \end{equation}  
%  where $\beta = (1 + \alpha)$ and $x_{min}$ is the smallest measured value of $x_i$.~\cite{meroz_toolbox_2015,clauset_power-law_2009}
%  proportional to $t^{-1-\alpha}$.~\cite{meroz_toolbox_2015}
  Because we are limited to taking measurements at discrete intervals dictated by the output 
  frequency of our simulation trajectories, we fit the empirical dwell times
  to a discrete power law distribution whose maximum likelihood $\alpha_d$ 
  parameter we calculated by maximizing the following likelihood function: 
  \begin{equation}
	\mathcal{L}(\beta) = -n\ln \zeta(\beta, t_{min}) -
	\beta\sum_{i=1}^{n} \ln t_i 
  \label{eqn:powerlaw_likelihood}
  \end{equation}
  where $\beta = 1 + \alpha_d$, $t_i$ are collected dwell time data points,
  $n$ the total number of data points, and $\zeta$ is the Hurwitz zeta function
  where $t_{min}$ is the smallest measured value of	$t$.~\cite{clauset_power-law_2009}

@@

  % BJC3: Making a logical argument regarding how we estimate H here is important
  % because I haven't seen anyone do it this way.
  sFBM implies that hops are correlated which we describe using the Hurst parameter, $H$. 
  The autocovariance function of hop lengths has the analytical form:~\cite{mandelbrot_fractional_1968}
  \begin{equation}
    \gamma(k) = \dfrac{\sigma^2}{2}\bigg[|k-1|^{2H} - 2|k|^{2H} + |k+1|^{2H}\bigg]
  \label{eqn:fbm_autocorrelation}
  \end{equation}
  where $\sigma^2$ is the variance of the underlying Gaussian distribution from which hops are
  drawn and $k$ is the time lag, or number of increments between hops. The hop autocorrelation
  function is simply Equation~\ref{eqn:fbm_autocorrelation} normalized by the variance. 
  When $H < 0.5$, hops are negatively correlated, when $H = 0.5$ we recover Brownian motion
  and when $H > 0.5$, one observes positive correlation between hops. There are many methods
  for estimating the Hurst parameter for a time series.~\cite{clegg_practical_2006} It can
  be a difficult task because Equation~\ref{eqn:fbm_autocorrelation} decays slowly to zero, 
  especially when $H > 0.5$, meaning one needs to study large time lags with high frequency.
  Fortunately (from a mathematical perspective), all of our solutes show anti-correlated motion, so most of the information in
  Equation~\ref{eqn:fbm_autocorrelation} is contained within the first few time lags (see 
  Figure~\ref{S-fig:hurst_autocorrelation} of the Supporting Information). Any hope of
  fitting longer time lags to our data is lost in the noise since the analytical values
  are so close to zero. Therefore, we obtained H by performing a least squares fit of 
  Equation~\ref{eqn:fbm_autocorrelation} to the first 10 lags of the empirically measured
  autocorrelation function.

@@

  We observe different dynamical behavior when solutes move while inside 
  the pore versus while in the tail region. This inspired two anomalous diffusion 
  models of varying complexity. We created a simple, single mode model with a single 
  set of parameters fit to solute trajectories.
%  $\alpha$, $\sigma$, $H$ and, when the truncated power law is used, $\lambda$ parameters
%  fit to solute trajectories.
  Our second, two mode model assigns a set of parameters to each of 2 modes based
  on the solute's radial location. Solutes in mode 1 are in the pore region, defined
  %MRS4: some justification on why 0.75 vs. any other cutoff.
  %BJC4: I justified sentence after next. 
  as less than 0.75 nm from any pore center. All else are in mode 2, the tail region. 
  We determined this cut-off by maximizing the difference in dynamical behavior as 
  described in our previous work.~\cite{coscia_chemically_2019} Unfortunately, 
  there were not enough sufficiently long sequences of hops in each mode to reliably
  calculate a Hurst parameter for each mode so we used the Hurst parameter from the 
  single mode model for both modes of the two mode model.

@@

  We simulated models with all combinations of the types of dwell and hop length
  distributions described above, which are summarized in Table~\ref{table:anomalous_models}.
  All models include correlation between hops.
  %MRS4: not abbreviations are not necessarily defined: should be defined above, perhaps? (i.e. we will refer X as 'sFBMcut')
  %BJC4: made table
  \begin{table}[!htb]
	  \centering
	  \begin{tabular}{|c|c|c|}
	  \hline
	  Dwell Distribution                & Hop Length Distribution & Abbreviation \\
	  \hline
      Power Law                         & Gaussian                & sFBM         \\
      Power Law w/ Exponential Cut-off  & Gaussian                & sFBMcut      \\
      Power Law                         & L\'evy Stable           & sFLM         \\
      Power Law w/ Exponential Cut-off  & L\'evy Stable           & sFLMcut      \\
	  \hline
	  \end{tabular}
	  \caption{We tested models with various modifications to the dwell and hop
	  length distributions. We incorporate correlation structure into all models.}\label{table:anomalous_models}
 \end{table}

  % BJC3: will need to modify this text to reflect different lengths of simulations
  For each solute, we simulated 10,000 anomalous diffusion trajectories of length
  $T_{sim}$ in order to directly compare our model's predictions to MD simulations.
  $T_{sim}$ varied due to differing solute equilibration times. We constructed 
  trajectories by simulating sequences of dwell times and correlated hop lengths
  generated based on parameters randomly chosen from our bootstrapped parameter 
  distributions. We propagated each trajectory until the total time equaled or 
  exceeded $T_{sim}~ \mu$s, then truncated the last data point so that the total 
  time exactly equaled $T_{sim}~ \mu$s since valid comparisons are only possible 
  between fixed length sFBM simulations. 
  % BJC4: removed following sentence because I talk about aging above
  %The power law dwell time behavior gives rise to the aging phenomenon, embodied by a 
  %decrease in MSD with measurement time.~\cite{neusius_subdiffusion_2008,metzler_anomalous_2014}
  We reported the time-averaged MSD after time lags 40\% the length of the trajectory
  with corresponding 95\% confidence intervals.
  When simulating 2 mode models, we determined the state sequence based on random 
  draws weighted by the appropriate row of the probability transition matrix. We 
  drew hops and dwells based on the current state of the system. Since we calculated
  the transition probabilities from a finite data set, they have an associated 
  uncertainty which we 
  %MRS4: not quite sure what you mean by incorporating uncertainty. 
  %BJC4: Added comment about having a finite amount of data with which to create transition matrix. Therefore it is uncertain
  incorporated by re-sampling each row from a two dimensional Dirichlet distribution
  (also called a beta distribution for the 2D case) with concentration parameters 
  defined by the count matrix.~\cite{bacallado_bayesian_2009}

@@

  %We also projected MSDs out to 1 second for each solute. % BJC3:??
  %BJC3: not sure how to cite fbm
  We used the python package \texttt{fbm} to generate exact simulations of FBM and our
  own python implementation of the algorithm by Stoev and Taqqu to simulate FLM.
  \cite{stoev_simulation_2004} Note that, to our knowledge, there are no known exact
  simulation algorithms for generating FLM trajectories, however, the algorithm
  we used sufficiently approximates draws from the marginal distribution and 
  reasonably approximates the correlation structure. We added an empirical correction
  to enhance the accuracy of the correlation structure (see Section~\ref{S-section:flm_correlation}
  of the Supporting Information for validation of the approach).

@@

%  BJC4: I already said this above
%  When simulating MD-length FLM trajectories, we limited the maximum hop length based on where
%  the empirical hop distribution began to significantly under-sample the theoretical
%  maximum likelihood estimate (MLE) L\'evy stable distribution (see 
%  Section~\ref{S-section:truncation} of the Supporting Information).

%  For our 1 second simulations, we limited the maximum hop length to that seen by
%  the same solute undergoing Brownian motion in an unconfined aqueous environment. 
%  We have no reason to believe there is any kind of facilitated diffusion, so 
%  excursions characteristic of Brownian motion represent a reasonable upper limit
%  on hop lengths. To determine these limits we placed 24 solutes in a cubic box of 
%  water, 4 nm on each side. We allowed the solutes to diffuse for 100 ns, more than
%  ensuring the mean squared displacement entered a linear regime. We recorded the largest
%  observed hop length over a 0.5 ns time lag.

@@

  A Markov state model (MSM) decomposes a time series into a set of discrete states
  with transitions between states defined by a transition probability matrix, $T$,
  which describes the conditional probability of jumping to a specific state given
  the previously observed state.~\cite{pande_everything_2010,wehmeyer_introduction_2018}
  Software packages such as MSMbuilder~\cite{beauchamp_msmbuilder2:_2011} and 
  pyEMMA~\cite{scherer_pyemma_2015} provide work flows capable of featurization and
  dimensional reduction which are often necessary to identify representative states.

@@

  %MRS4: here, be more explicit you are testing the validity of the Markovian approximation on the molecular data.
  %BJC4: Tried to clarify in thesis statement. Let me know if you think it needs more
  We verified the Markovianity of state transitions by solutes in our MD simulations 
  by analyzing the empirically measured transition matrix. An important condition
  of a Markov process is the satisfaction of detailed balance:
  \begin{equation}
  T_{i,j}P_i(t=\infty) = T_{j,i}P_j(t=\infty)
  \end{equation}
  where $P$ is the equilibrium distribution of states. In other words, the number of
  transitions from state $i$ to $j$ and from state $j$ to $i$ should be equal. A second
  test is to verify that $T$ holds up to coarser time scales. As long as solutes
  sufficiently sample the states in Table~\ref{table:states}, $T$ should be invariant
  with time.~\cite{swope_describing_2004} We verified these properties 
  in Section~\ref{S-section:markov_validation} of the Supporting Information.

@@

  \subsection{Solute Flux}

@@

  We further validated our models by training the parameters on half of the 
  equilibrated trajectories and then using them to predict the MSD calculated
  from the alternate half of the trajectories. We trained on both the first
  and second half of the data. At equilibrium, the parameter estimates should 
  be the same, within error, for either portion of the data used for training.
